Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-02-11 chapters/chapter02.tex
finishing touches

Figure~\ref{fig:collapsing} illustrates this action for a branch that spans a single boundary at known time $T_1$ with $\mathbf{Q}_1$ governing the process before the boundary and $\mathbf{Q}_2$ after the boundary. Letting $X(T_1) = k$ represent the augmented state of the stochastic process at the boundary, we compute

@@

\An interesting direction for further research using the epoch model is to couple epoch-specific parameters to external covariates.
For the within-host HIV data sets we analyze here, it may be interesting to ask whether $\omega$ varies with changes in CD4+ counts or viral load.
In our Bayesian framework, we can address this question through formulating a hierarchical phylogenetic model \citep{Edo-Matas2011} over the epoch-specific parameters, considering the covariates as fixed-effects. 
We can further estimate the posterior probabilities of all possible linear models that may or may not include the covariates using Bayesian stochastic search variable selection \citep{Kuo1998}.  
In addition to external covariates, we can also consider connecting the evolutionary parameters in an epoch model to population size parameters in non-parametric models of population size change through time, such as the Bayesian skyline \citep{Drummond2005}, skyride \citep{Minin2008b} and skygrid models \citep{Gill2013}.

>>>>

\myedit{svseventeen}{
Figure~\ref{fig:collapsing} illustrates this action for a branch that spans a single boundary at known time $T_1$ with $\mathbf{Q}_1$ governing the process before the boundary and $\mathbf{Q}_2$ after the boundary. Letting $X(T_1) = k$ represent the augmented state of the stochastic process at the boundary, we compute:
}

@@

An interesting direction for further research using the epoch model is to couple epoch-specific parameters to external covariates.
For the within-host HIV data sets we analyze here, it may be interesting to ask whether $\omega$ varies with changes in CD4+ counts or viral load.
In our Bayesian framework, we can address this question through formulating a hierarchical phylogenetic model \citep{Edo-Matas2011} over the epoch-specific parameters, considering the covariates as fixed-effects. 
We can further estimate the posterior probabilities of all possible linear models that may or may not include the covariates using Bayesian stochastic search variable selection \citep{Kuo1998}.  
In addition to external covariates, we can also consider connecting the evolutionary parameters in an epoch model to population size parameters in non-parametric models of population size change through time, such as the Bayesian skyline \citep{Drummond2005}, skyride \citep{Minin2008b} and skygrid models \citep{Gill2013}.
